% -------------------- EXPERIENCE --------------------
\section*{Experience}

\textbf{Ubisoft Entertainment} \hfill Pune, India \\
\textit{Build Engineer II} \hfill 05/2025 -- Present
\begin{itemize}
  \item Develop and maintain CI/CD pipelines and build/release workflows for the live-service title \textit{Skull and Bones}, supporting stable integration and patch delivery during live operations.
  \item Collaborate with engineering, QA, release, and infrastructure teams to improve build reliability, delivery speed, and developer productivity across critical environments.
  \item Automated Perforce copy-ups, merges, and integration validation checks, reducing integration-related failures by \textbf{~80--90\%}.
  \item Owned Ansible-based configuration management for on-prem build infrastructure, improving consistency and reducing configuration drift.
  \item Managed containerized workload migrations on Kubernetes using Helm, ensuring minimal downtime and consistent configuration across clusters.
  \item Diagnosed complex pipeline and environment issues through ELK-based log aggregation and analysis, improving failure visibility and operational stability.
\end{itemize}

\vspace{2pt}

\textbf{LightFury Games} \hfill Bangalore, India \\
\textit{Build Engineer II} \hfill 11/2024 -- 04/2025
\begin{itemize}
  \item Designed and implemented Android CI pipelines with automated preflight builds and tests, reducing manual intervention by \textbf{~30\%}.
  \item Defined Perforce branching strategies for pre-production environments and maintained a commit server to support distributed development workflows.
  \item Optimized Perforce performance across APAC using proxy and edge servers, reducing full workspace sync times from \textbf{~45 min to ~17 min}.
  \item Integrated AWS infrastructure components (EC2, ECS, ECR, IAM) with Google SSO to improve secure access and operational efficiency.
\end{itemize}

\vspace{2pt}

\textbf{Ubisoft Entertainment} \hfill Pune, India \\
\textit{Build Engineer} \hfill 09/2021 -- 11/2024
\begin{itemize}
  \item Owned and evolved CI/CD pipelines for AAA titles including \textit{Just Dance}, \textit{Skull and Bones}, \textit{Roller Champions}, and \textit{Monopoly Madness}.
  \item Led a migration to TeamCity using Kotlin DSL, improving the maintainability and scalability of build automation.
  \item Reduced deployment and delivery times by \textbf{~30\%} through pipeline optimization, automation, and reliability improvements.
  \item Partnered with development and release teams to troubleshoot build breakages, delivery blockers, and environment issues in production workflows.
\end{itemize}

\vspace{4pt}

\textbf{Ubisoft Entertainment} \hfill Pune, India \\
\textit{QA Engineer I} \hfill 01/2020 -- 08/2021
\begin{itemize}
  \item Automated test suites and authored test cases for \textit{For Honor}, improving regression coverage and release confidence.
  \item Collaborated closely with developers and build teams, building early experience in CI pipelines, issue triage, and root-cause analysis.
\end{itemize}
